---
title: "R Notebook"
output: html_notebook
---

# Code to Read In

### Code for Wget Files

2 Shell Scripts for Reading Files
* Submit.sh
* getData.sh

__Code from getData.sh__
#!/bin/bash

n=$SLURM_ARRAY_TASK_ID


numid=$((2018+$n))

for i in 01 02 03 04 05 06 07 08 09 10 11 12
do
#if ($i <= 9)
#then
#wget https://d37ci6vzurychx.cloudfront.net/trip-data/fhvhv_tripdata_$numid-0$i.parquet
#else
wget https://d37ci6vzurychx.cloudfront.net/trip-data/fhvhv_tripdata_$numid-$i.parquet
#fi
done

### Converting Parquet to CSV

```{r}
install.packages("arrow")

library(arrow)

```

```{r}
parquet_file <- "fhvhv_tripdata_2020-05.parquet"

df <- read_parquet(parquet_file)

csv_file <- "fhvhv.csv"

write.csv(df, file = csv_file, row.names = FALSE)

```

# Variables


# Statistical Methods

* Data Analysis- Which company performs best
* Regression



# Computational Steps 

* Data Collection- pull Data from Kaggle (wget)
* Data Cleaning- Convert all Parquet files to CSV (Create some metrics for data conversion to ensure that no data is lost)
* Potentially some Feature Engineering
* Questions- begin to create code to address questions
* Pick one question for proposal

