---
title: "R Notebook"
output: html_notebook
---
# Group Members
Peter Harmer
Abhimanyu Dev Gupta


# Github Repository
https://github.com/jmbost20/Stat405Project

# Data Source
https://www.kaggle.com/datasets/jeffsinsel/nyc-fhvhv-data

# Code Snippets

### Code for Wget Files

2 Shell Scripts for Reading Files
* Submit.sh
* getData.sh

### Code from getData.sh
#!/bin/bash

n=$SLURM_ARRAY_TASK_ID


numid=$((2018+$n))

for i in 01 02 03 04 05 06 07 08 09 10 11 12
do
#if ($i <= 9)
#then
#wget https://d37ci6vzurychx.cloudfront.net/trip-data/fhvhv_tripdata_$numid-0$i.parquet
#else
wget https://d37ci6vzurychx.cloudfront.net/trip-data/fhvhv_tripdata_$numid-$i.parquet
#fi
done

### Converting Parquet to CSV

```{r}
install.packages("arrow")

library(arrow)

```

```{r}
parquet_file <- "fhvhv_tripdata_2020-05.parquet"

df <- read_parquet(parquet_file)

csv_file <- "fhvhv.csv"

write.csv(df, file = csv_file, row.names = FALSE)

```

# Variables
* Hvfhs_license_num: This variable identifies the business a particular trip was associated with.
* Tips: This variable measures the total tip recieved by the driver from the customer. 
* trip_miles: This variable simply measures the length of the trip in miles. 
* tolls: This variable simply measures the amount paid in tolls in the trip.
* driver_pay: This measures the total pay the driver recieves, not including tolls, tips, taxes or surcharges. 
* sales_tax: The NYC sales tax levied on each trip. 
* congestion_surcharge: The amount collected for congestion surcharge. 
* Pickup_datetime: This represents the date and time of the pickup.
* DropOff_datetime: This represents the date and time of the drop off.
* request_datetime: The time the customer requested to be picked up. 
* on_scene_datetime: The time the driver arrived at the pickup location.
* There are many more variables, however at this point these seem the most relevant to our question.

# Questions
What values produce the most profit for the driver?
	- Does a particular company/app have better payed drivers?
	- Is any particular time of year better than another?
	- Does length of trip actually have an affect on profit?
	- Does the time of year affect profit?
	

## Statistical Methods

### Data Analysis:
* Create graphs that focus on displaying differences in driver pay and performance for each ride-sharing service
* Create graphs that display correlation between certain variables and driver pay

### Regression:
* Use linear and/or Polynomial regression to identify the variables that have the largest impact on driver pay.
* Implement regression lines into analysis graphs to show a visual relationship between different variables and driver pay.


# Computational Steps 

* Data Collection- pull Data from Kaggle (wget)
* Data Cleaning- Convert all Parquet files to CSV (Create some metrics for data conversion to ensure that little to no data is lost)
* Process data by individual year and/or month (or if need be even more granularly) using HPC. This could include removing unecessary variables, sorting the data by a variable like company.
* Potentially some Feature Engineering
* Questions- Create code to address the primary question and sub questions using the now processed data

