---
title: "R Notebook"
output: html_notebook
---
# Group Members
Peter Harmer
Abhimanyu Dev Gupta
Jonah Bostrom


# Github Repository
https://github.com/jmbost20/Stat405Project

# Data Source
https://www.kaggle.com/datasets/jeffsinsel/nyc-fhvhv-data

# Code Snippets

### Code for Wget Files

2 Shell Scripts for Reading Files
* Submit.sh
* getData.sh

### Code from getData.sh
#!/bin/bash

n=$SLURM_ARRAY_TASK_ID


numid=$((2018+$n))

for i in 01 02 03 04 05 06 07 08 09 10 11 12
do
#if ($i <= 9)
#then
#wget https://d37ci6vzurychx.cloudfront.net/trip-data/fhvhv_tripdata_$numid-0$i.parquet
#else
wget https://d37ci6vzurychx.cloudfront.net/trip-data/fhvhv_tripdata_$numid-$i.parquet
#fi
done

### Converting Parquet to CSV

```{r}
install.packages("arrow")

library(arrow)

```

```{r}
parquet_file <- "fhvhv_tripdata_2020-05.parquet"

df <- read_parquet(parquet_file)

csv_file <- "fhvhv.csv"

write.csv(df, file = csv_file, row.names = FALSE)

```

# Variables
* Hvfhs_license_num: This variable identifies the business a particular trip was associated with.
* Tips: This variable measures the total tip recieved by the driver from the customer. 
* trip_miles: This variable simply measures the length of the trip in miles. 
* tolls: This variable simply measures the amount paid in tolls in the trip.
* driver_pay: This measures the total pay the driver recieves, not including tolls, tips, taxes or surcharges. 
* sales_tax: The NYC sales tax levied on each trip. 
* congestion_surcharge: The amount collected for congestion surcharge. 
* Pickup_datetime: This represents the date and time of the pickup.
* DropOff_datetime: This represents the date and time of the drop off.
* request_datetime: The time the customer requested to be picked up. 
* on_scene_datetime: The time the driver arrived at the pickup location.
* There are many more variables, however at this point these seem the most relevant to our question.

# Questions
What values produce the most profit for the driver?
	- Does a particular company/app have better payed drivers?
	- Is any particular time of year better than another?
	- Does length of trip actually have an affect on profit?
	- Does the time of year affect profit?
	

## Statistical Methods

### Data Analysis:
To depict our analyses we will create graphs that display the difference in driver pay and performance between different companies/services,
as well as display the correllation between different variables and driver pay

### Regression:
We plan to use linear and/or Polynomial regression to identify the variables that have the largest impact on a drivers pay/profit.
Additionally, on the graphs depicting our analysis we will add regression lines to visually show the relationship between different variables and driver pay.


# Computational Steps 
To accomplish this we will pull our data from Kaggle (wget), convert it from Parquet format to CSV while ensuring little to no data is lost,
process it into year, month, and/or company blocks using the HPC. This processing could include pruning unecessary variables or sorting the data.
We may also perform some featuring engineering if required. Finally we will create code to address the primary and sub questions using the now processed and cleaned data.
